\documentclass[preprint,12pt]{elsarticle} %review, or preprint

\usepackage{amssymb}
\usepackage{graphics}
\usepackage{float}
\usepackage[normalem]{ulem}
\usepackage{color}


\graphicspath{{./Images/}}

\journal{Solar Energy Materials \& Solar Cells}

\begin{document}

\begin{frontmatter}

\title{Life Cycle Assessment of Dynamic Building Integrated Photovoltaics} 

\author[ita]{P. Jayathissa\corref{cor2} \tnoteref{t1}}
    \ead{jayathissa@arch.ethz.ch}
\address[ita]{Architecture and Building Systems, Institute of Technology in Architecture, Department of Architecture,\\ ETH Zurich, Switzerland} 
% For whatever reason the affiliation needs to be defined after the authors. Otherwise the numbering gets messed up.

\author[ita]{M. Jansen\tnoteref{t1}}
    \ead{m.jansen@student.ethz.ch}

\author[baug]{N. Heeren}
    \ead{heeren@ifu.baug.ethz.ch}
\address[baug]{Ecological System Design, Institute of Environmental Engineering,\\ ETH Zurich, Switzerland}

\author[ita]{Z. Nagy}
	\ead{nagy.arch.ethz.ch}

\author[baug]{S. Hellweg}
	\ead{hellweg@ifu.baug.ethz.ch}


\author[ita]{A. Schlueter \corref{cor1} }
    \ead{schlueter@arch.ethz.ch}

\tnotetext[t1]{Equally contributing first authors} 
\cortext[cor2]{Corresponding author}


\begin{abstract}
In this paper we assess the environmental impact of dynamic, adaptive building integrated photovoltaic (BIPV) solutions. Such a system combines the benefits of adaptive shading, thus reducing the building energy demand, and facade solar tracking that increases electricity production. The inventory was acquired using production data, and Energy Plus simulations to calculate the building energy demand. The impact assessment was conducted according to ISO 14040 and ISO 14044 standards using the ecoInvent database and openLCA as an analysis tool. The embodied environmental impact of a dynamic BIPV solution is three times worse than a static solution due to the added control system, electronics, actuators, and additional supporting structure. However the added savings through adaptive shading to the buildings heating, cooling and lighting loads offsets the entire embodied environmental impact threefold. This demonstrates the advantage of using the PV material, not only as an electricity generation unit, but also as a building material for adaptive shading systems. We also conduct a sensitivity analysis looking at modifications to the actuator type, and the control system. The greatest influence on the result was the emission factor of the electricity mix where the building is located. The analysis ultimately enables us to provide design recommendations for future dynamic BIPV installations. 

\end{abstract}

\begin{keyword}
\sep Dynamic Photovoltaics \sep Life Cycle Analysis \sep Multi Functional Envelope \sep BIPV \sep Adaptive Shading
\end{keyword}

\end{frontmatter}

\section{Introduction}
\label{ch:introduction}
\input{1_introduction}

\section{Methodology}
\label{ch:method}
\input{2_methodology}

\section{Results}
\label{ch:results}
\input{3_results}


\section{Discussion}
\label{ch:discussion}
\input{5_discussion}

\section{Conclusion}
\label{ch:conclusion}
\input{6_conclusion}

\section{Acknowledgments}
\label{ch:acknowledgments}
\input{7_acknowledgments}

\section{Appendix}
\label{ch:appendix}
\input{8_appendix}

%% appendix sections are then done as normal sections
%% \appendix
%% \section{}
%% \label{}

%% bibitems, please use
  \bibliographystyle{elsarticle-num} 
  \bibliography{references}

\end{document}
\endinput